### 2022-11-10 paper-thesis/chapters/01-introduction.tex
A bit of more writing

This goal of this paper is to investigate how well Statix is fit for the task of defining a simple dependently-typed language. We want to investigate whether typical features of dependently typed languages can be encoded concisely in Statix. The goal is not only to show that Statix can implement it, but to investigate whether implementing a dependent type checker is easier in Statix than in a general-purpose programming language.

>>>>

\section{Contributions}
This goal of this paper is to investigate how well Statix is fit for the task of defining a simple dependently-typed language. We want to investigate whether typical features of dependently typed languages can be encoded concisely in Statix. The goal is not only to show that Statix can implement it, but to investigate whether implementing a dependent type checker is easier in Statix than in a general-purpose programming language.

The technical contributions of this thesis are the following:
\begin{itemize}
	\item 
\end{itemize}

\section{Outline}

### 2022-11-10 paper-thesis/chapters/30-comparing-with-haskell.tex
A bit of more writing

\begin{lstlisting}
[NType(Var(0)), NType(Type())]
\end{lstlisting}
\begin{tikzpicture}[scopegraph, node distance = 2.5em and 2.5em]
	\node[scope] (s1) {$s1$};
	\node[type, above of = s1] (s1l) {$\texttt{T : Type()}$};
	\draw (s1) edge[type] (s1l);

@@

@@

>>>>

\begin{lstlisting}
NType(Var(0)) :: NType(Type()) :: Nil
\end{lstlisting}
\begin{tikzpicture}[scopegraph, node distance = 2.5em and 2.5em]
	\node[scope] (s1) {$s1$};
	\node[type, above of = s1] (s1l) {$\texttt{T : Type()}$};
	\draw (s1) edge[type] (s1l);

@@

The nodes in scope graphs may have multiple children, but we never query the children of a node. We only follow the edges, we don't go in the opposite direction. Similarly, part of a list may be shared, but this is fine in Haskell, since values are immutable.

@@

Now we want to define beta head reduction. Remember that in Statix, beta head reduction is a relation with the signature
\begin{lstlisting}
betaReduceHead : 
	(scope * Expr) * list((scope * Expr)) -> (scope * Expr)
\end{lstlisting}
